---
title: "Administrative boundaries of Belgium based on OpenStreetMap data"
author: "Jan Wijffels"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Administrative boundaries of Belgium based on OpenStreetMap data}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

An Introduction to **BelgiumMaps.Admin** package
=======================================


```{r setup, include=FALSE}
library(knitr)
opts_chunk$set(out.extra='style="display:block; margin: auto"', fig.align="center")
```

Introduction
------------

The  **BelgiumMaps.Admin** package contains maps of administrative boundaries of Belgium extracted from OpenStreetMap. This data is available in the BE_OSM_ADMIN object.

```{r dataset}
library(sp)
library(BelgiumMaps.Admin)
data(BE_OSM_ADMIN)
class(BE_OSM_ADMIN)
str(BE_OSM_ADMIN@data)
```


Visualisation
----------------------------
This package contains administrative boundaries at different levels (national, regional, provinces, districts, municipalities and sections).

```{r basic plots}
plot(BE_OSM_ADMIN)
plot(subset(BE_OSM_ADMIN, admin.level %in% "2"), main = "National")
plot(subset(BE_OSM_ADMIN, admin.level %in% "4"), main = "Regions")
plot(subset(BE_OSM_ADMIN, admin.level %in% "6"), main = "Provinces")
plot(subset(BE_OSM_ADMIN, admin.level %in% "7"), main = "Districts")
plot(subset(BE_OSM_ADMIN, admin.level %in% "8"), main = "Municipalities")
## Boundaries at the level 9 seem to be incomplete
plot(subset(BE_OSM_ADMIN, admin.level %in% "9"), main = "NISsections")
```


Integrate with BelgiumStatistics
----------------------------
The data also contains NIS codes which can be used to link against the data in the BelgiumStatistics package. This package can be found at https://github.com/jwijffels/BelgiumStatistics. Examples about this can be found in that package.


